\section{Chaining Mechanism}

\subsection{Author List}  Reviewing will be double-blind; therefore, please do not include any author names on any submitted documents except in the space provided on the submission form. You must also ensure that the metadata included in the PDF does not give away the authors. If you are improving upon your prior work, refer to your prior work in the third person and include a full citation for the work in the bibliography. For example, if you are building on your own prior work in the papers~\cite{nicepaper2,nicepaper3}, you would say something like: ``While prior work did X, Y, and Z~\cite{dca,gem5-gpu}, this paper additionally does W, and is therefore much better.'' Do not omit or anonymize references for blind review. There is one exception to this for your own prior work that appeared in IEEE CAL, workshops without archived proceedings, etc., as discussed later in this document.

Recall that, per IEEE authorship guidelines, it is not acceptable to award honorary authorship or gift authorship. Please keep these guidelines in mind while determining the author list of your paper. Also please note that addition/removal of authors once the paper is accepted will have to be approved by the Program Chair.

\subsection{Figures and Tables}

Ensure that the figures and tables are legible. Please also ensure that you refer to your figures in the main text. Many reviewers print the papers in gray-scale. Therefore, if you use colors for your figures, ensure that the different colors are highly distinguishable in gray-scale.
