\section{Results}

Authors must register all their conflicts on the paper submission site. Conflicts are needed to ensure appropriate assignment of reviewers. If a paper is found to have an undeclared conflict that causes a problem OR if a paper is found to declare false conflicts in order to abuse or game the review system, the paper may be rejected.

Please declare a conflict of interest with the following people for any author of your paper.
A conflict occurs in the following cases:
\begin{enumerate}
\item Between advisor and advisee forever. 
\item Between family members forever. 
\item Between people who have collaborated in the last 5 years. This collaboration can consist of a joint research or development project, a joint paper, or when there is direct funding from the potential reviewer (as opposed to company funding) to an author of the paper. Co-participation in professional activities, such as tutorials or studies, is not cause for conflict. When in doubt, the author should check with the PC chair. 
\item Between people from same institution or who were in the same institution in the last 5 years. 
\item Between people whose relationship prevents the reviewer from being objective in his/her assessment
\end{enumerate}


``Service'' collaborations, such as co-authoring a report for a professional organization, serving on a program committee, or co-presenting tutorials, do not themselves create a conflict of interest. Co-authoring a paper that is a compendium of various projects with no true collaboration among the projects does not constitute a conflict among the authors of the different projects.

We hope to draw most reviewers from the PC and the ERC, but others from the community may also write reviews. Please declare all your conflicts (not just restricted to the PC and ERC). When in doubt, contact the Program Chair.
