\section{Motivation} \label{motivation}
As seen in section \ref{introduction}, incorporating GPU into the same die as CMPs provides for several advantages and the use of this as a general purpose computing resource is gaining traction in applications. In line with the goals of IHS processors, we propose the addition of a large capacity stacked DRAM between CPU and GPU. This capacity will be used as a last level cache before accessing the off-chip DRAM. The large bandwidth provided by these devices will help the GPU and the modest reduction in access latency can improve the performance of CPU. However, the organization of the DRAMCache for this type of heterogeneous processors is not immediately intuitive.
Due to the requirement of large storage, of order of the last level SRAM caches for hundreds of MBs of DRAMCaches, prior works have placed metadata alongside the data in the DRAM devices. These designs have focused on improving access latencies for the accesses using structures to predict cache line residency and removing the tag-serialization overhead by overlapping access or storing tags with data.
Firstly, associativity is known to improve cache hit rates by reducing conflict misses. However in DRAMCaches associativity comes at a cost of increased hit latencies due to the tag requiring to be burst out of the stacked DRAM. Hence there is an implicit trade-off between providing better hit-rates and reduced access latency. A higher associativity design is suitable for a GPGPU processor which can trade increased access latency for higher hit rates and use the larger bandwidth of the DRAMCache. On the other hand, a CPU would suffer when using such a design but would benefit from a latency-optimized direct-mapped cache \cite{alloy-cache}. Secondly, due to the large number of requests from the GPUs at the DRAMCache, the DRAMCache will predominantly be occupied by GPU lines starving the CPU of the latency benefits from the DRAMCache. Thirdly, the CPU requests will encounter large queuing latencies as the GPU inherently exploits good locality within DRAMCache.



\input{motivation-ipc-hit-rate}