My experience at IISc has been nothing short of incredible and several thanks are in order.
\par First and foremost, I would like to express my deeprest gratidude to my research advisor Prof. R. Govindarajan for being a supportive mentor and guide. He has been patient with me and has encouraged, taught and motivated me to think clearly and critically. His humbleness, knowledge and relentless work ethic will always be a constant source of inspiration to me.
\par I owe a deep sense of gratitude to everyone who have made my stay at IISc comfortable. A big thanks to the department chairman Professor Jayant Haritsa and Professor Uday Reddy whose backing and ecouragement towards student system admin activities and their endorsement for compute infrastructure make the department well equipped to perform research. I am grateful to the staff at CSA office and the system admins Jagdish and Pushparaj who work tirelessly to keep the department and compute resources running. Thanks are also due for the funding sources - MHRD and AMD for supporting me financially to take care of my day-to-day expenses. I have greatly enjoyed courses by Professor Matthew Jacob and Professor Jayant Haritsa and their refreshing ways of course instruction.
\par I also want to acknowledge everyone in the HPC lab - Jayvant, Shilpa, Abhinav, Nagendra and Arth for providing a friendly and constructive atmosphere in the lab and for their useful feedback and insightful comments on my work. It was great sharing lab discussions and deliberating over problems and findings. My thanks also go out to my wonderful friends at IISc - Arvind, Vinay, Sridhar, Srinidhi, Anirudh, Pallavi, Sathya, Divya and several others who are not mentioned here. It was a pleasure sharing the many meals, dinner and ice cream outings and the lively banter in the mess. You always made sure there was never a dull moment and made my stint here truly memorable.
\par I would also like to thank Vikram, Archana, Aditya, Divyanshu and the members of IISc Running Club for organizing wondeful running events on campus and giving me a chance to represent the institute at the 12 hour relay run. It was wonderful being running buddies with all of you. I will always fondly remember my morning runs at this wondeful and serene campus which provided a harmonious evironment throughout the year and has always reinvigorated and rejuvenated my spirits in silence.
\par I must express my profound gratitude to my parents for their unconditional support for all my decisions, their counsel and lending me a sympathetic ear when I needed it. Finally, I thank Kumudha who has always been there for me, be it for technical advice or moral support. Her unyielding love has been my source of strength. My gratitude also goes to my parents-in-law who have been so supportive of us.\\
\\
\par Thank you very much, everyone!